---
title: "Simple seasonality plot"
author: "John Kubale"
date: "11/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r ,echo=T,results='hide', message=FALSE, warning=FALSE}
library(rvest)
library(dplyr)
library(lubridate)
library(tidyr)
library(ggplot2)
library(scico)
# library(tidyquant)
```

# Scrape RSV surveillance data from CDC 

```{r, echo=T,message=FALSE, warning=FALSE}
url <- "https://www.cdc.gov/surveillance/nrevss/images/trend_images/RSV14Num_Nat.htm"

rsvdata <- url%>%
  read_html()%>%
  html_nodes(xpath = "/html/body/table")%>%
  html_table()%>%
  .[[1]]

head(rsvdata)

rsvdata <- rsvdata%>%
  rename(week = "")%>%
  mutate(Antigen = as.numeric(`Antigen Detections`),
         PCR = as.numeric(`PCR Detections`),
         wk_date = as_date(RepWeekDate, 
                           format = guess_formats(RepWeekDate, "mdy")[1]))%>%
  select(week, wk_date, Antigen, PCR)


```
\

# Make simple bar chart of RSV PCR detections over time
```{r}
ggplot(rsvdata)+
  geom_bar(aes(x = wk_date, y = PCR), stat = "identity", fill = "navy")+
  scale_x_date(date_labels="%b-%Y", date_breaks="2 months")+
  labs(y = "Number of Detections per Week", x = "", title = "US RSV Detections by PCR")+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

```
\

# Include data on the number of antigen tests as well
First we need to transform the data to "long form" (i.e. 2 rows per week -- 
one with the number of PCR detections and the other with the number of antigen 
detections).
\
```{r, echo=F, include=F,message=FALSE, warning=FALSE}

rsvdata_long <- rsvdata%>%
  pivot_longer(-c(week, wk_date), names_to = "test_type", values_to = "count")

```
\

## Stacked 
```{r, echo=F, include=T, message=FALSE, warning=FALSE}
ggplot(rsvdata_long)+
  geom_bar(aes(x = wk_date, y = count, fill = test_type), stat = "identity", )+
  scale_x_date(date_labels="%b-%Y", date_breaks="2 months", expand=c(0,0))+
  labs(y = "Number of Detections per Week", x = "", title = "US RSV Detections by Test Type")+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.title = element_blank())
```
\
## Change the fill colors of the plot.
\
```{r, echo=F, include=T, message=FALSE, warning=FALSE}
ggplot(rsvdata_long)+
  geom_bar(aes(x = wk_date, y = count, fill = test_type), stat = "identity", )+
  scale_x_date(date_labels="%b-%Y", date_breaks="2 months", expand=c(0,0))+
  labs(y = "Number of Detections per Week", x = "", title = "US RSV Detections by Test Type")+
  scale_fill_scico_d(palette = 'vik')+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.title = element_blank())


```
\

## Stacked 
```{r, echo=F, include=T, message=FALSE, warning=FALSE}
ggplot(rsvdata_long)+
  geom_bar(aes(x = wk_date, y = count, fill = test_type), position = "dodge", stat = "identity", )+
  scale_x_date(date_labels="%b-%Y", date_breaks="2 months", expand=c(0,0))+
  tidyquant::coord_x_date(xlim = c("2020-01-01", "2021-01-01"))+
  labs(y = "Number of Detections per Week", x = "", title = "US RSV Detections by Test Type")+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.title = element_blank())
```
\
## Change the fill colors of the plot.
\
```{r, echo=F, include=T, message=FALSE, warning=FALSE}
ggplot(rsvdata_long)+
  geom_bar(aes(x = wk_date, y = count, fill = test_type), position = "dodge", stat = "identity", )+
  scale_x_date(date_labels="%b-%Y", date_breaks="2 months", expand=c(0,0))+
  labs(y = "Number of Detections per Week", x = "", title = "US RSV Detections by Test Type")+
  scale_fill_scico_d(palette = 'vik')+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.title = element_blank())
```


